A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-19 paper/draft.tex
create histogram of partisan spells
fix code for filtering active partisans

It is important to note that the affiliation of party members has been increasing over time. Importantly, this evolution has been rather rapid over time. While in the year 1997 there were around 200 thousand active party members, by the year 2018 this has increased to 10 million. While the causes of this rapid increase are not clear, it is most likely due to both increased registration and better quality data on partisan affiliation as the collection of information by the national electoral authority.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:map_pooled}
\end{figure}

Another interesting feature to note in the data is that there are discontinuities in the number of party members. The dashed lines indicate the year of a local election in Brazil, such as 2002 or 2018. The jumps in party affiliation are expressive, in particular for earlier electoral cycles. In particular, for the electoral year of 2002, there were around 2 million new party members registered as a result of that particular local election. While these jumps have decreased in more recent elections, it is an empirical regularity that highlights the electoral motivation driving party affiliation in Brazil.

>>>>

It is important to note that the affiliation of party members has been increasing over time. Figure \ref{fig:number_partisanship} illustrates this pattern. The growth in the number of partisan affiliates has been rather rapid over time. While in the year 1997 there were around 200 thousand active party members, by the year 2018 this has increased to 10 million. While the causes of this rapid increase are not clear, it is most likely due to both increased registration and better quality data on partisan affiliation as the collection of information by the national electoral authority.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:number_partisan}
\end{figure}

Another interesting feature to note in the data is that there are discontinuities in the number of party members. The dashed lines indicate the year of a local election in Brazil, such as 2002 or 2018. The jumps in party affiliation are expressive, in particular for earlier electoral cycles. For instance, in the electoral year of 2002, there were around 2 million new party members registered as a result of that particular local election. While these jumps have decreased in more recent elections, it is an empirical regularity that highlights the electoral motivation driving party affiliation in Brazil.

Regarding partisan duration spells, a few patterns emerge as in the . The spikes every four years mirror the jumps in partisanship in Figure \ref{fig:number_partisan} are mirrored
